---
title: "Playing with Linear Models"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Linear Model Viewer


```{r linear_model, echo=FALSE}
library(shiny)

ui <- shinyUI(pageWithSidebar(
  headerPanel("Visualizing Random Data about a Line"),
  sidebarPanel(
    sliderInput('intrcept', 'Choose intercept',value = 10, min = -20, max = 100, step = 5,),
    sliderInput('slope', 'Choose a slope',value = 0.33, min = 0, max = 2, step = 0.05,),
    sliderInput('nrands', 'Number of random points',value = 375, min = 50, max = 500, step = 10,),
    sliderInput('sdev', 'Standard deviation of random error',value = 50, min = 10, max = 100, step = 5,)
  ),
  mainPanel(
    plotOutput('newPlot'),
    h3('model R squared:'),
    textOutput("mdlfit")
  )
))

server <- function(input, output) {
    
    xcl <- reactive({
      runif(input$nrands, 0,500)
    })  
    
    ycl <- reactive({
      input$intrcept + input$slope * xcl() + rnorm(input$nrands, 0, input$sdev)
    })  
    
    modlcl <- reactive({
      lm(ycl() ~ xcl(), data=data.frame(ycl(),xcl()))
    })  
    
    output$newPlot <- renderPlot({
      plot(xcl(), ycl(), xlab='x value', col='lightblue',main='The Model', xlim=c(-25,max(xcl())), ylim=c(-50,500))
      abline(modlcl(), col="green",lwd=3)
      
    })
    
    output$mdlfit <- renderText({
      summary(modlcl())$r.squared
    })  
    
  }
shinyApp(ui = ui, server = server)
options = list(height = 1500)

```


Column {data-width=350}
-----------------------------------------------------------------------

### Documentation Panel

To use the application move the sliders on the left.
Watch the changes that happen in the plot.

The application does the following as a reaction to changing a slider value:   
1.  calculate a new set of random points   
2.  fit a linear model and draw the fitted line over the plot.   
3.  display the R-squared value for the model   


The Panel on the left provides the following:   

* Main panel: a plot of some generated random data points   
* Sidebar panel: a group of sliders that allow the parameters to be adjusted within fixed ranges
* Output: the R-squared value for the current model fit to the current set of data points

Main panel - the plot displays a number of randomly generated points.
The x values are uniformly distributed on a range from 0 to 500.
The y values are calculated using the following equation. 

    y = a + b * x + e
    
Where:   
a - the constant intercept at x = 0   
b - the slope   
x - the random uniform data   
e - a normal distributed random value with standard deviation set by the slider   



### Links

[Source code on Github](https://github.com/alanjl/dataprodassignment)
